Refined Flare Rates for Stars Younger than 250\,Myr

### 2023-09-27 src/tex/ms.tex
more additions

@@

This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}}
\citep{luger2021}, which promotes reproducible publications.

>>>>

There is a $3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21}
and the work presented here at ages $\sim 120$\,Myr. This discrepancy could be the
result of several factors. First, \cite{ilin21} used the \textit{K2} 30-minute
light curves. This would result in a sample biased towards the highest-energy flares which
could be sampled at this cadence. Our flare detection method is less-biased towards
the low-energy flares due to the 2-minute cadence from TESS and our flare detection
algorithm. Second, our sample has $\sim 2\times$ the number
of stars and $\sim 7\times$ the number of flares than their sample. This could
result in a more complete FFD compared to previous work.

@@

In this work, we present the first measured flare rates for stars $< 300$\,Myr using
TESS 2-minute cadence observations. We identified originating 28,822 flares from
3,983 stars. The results of our work are summarized as follows:

\begin{enumerate}
  \item We measured the flare-frequency distribution (FFD) slope, $\alpha$, for samples
  of flares binned by age and $T_\textrm{eff}$. We find $\alpha$ saturates at
  $\alpha = -0.5$ for stars younger than 300\,Myr and declines after that age.
  This is the first evidence that, like other tracers of stellar magnetic activity,
  flare rates saturate across spectral types.
  \item We measured the y-intercept, $\beta$, for the same bins of flares. We find
  that ...
  \item We measured the rotation periods, $P_\textrm{rot}$ for \textcolor{red}{n}
  stars in our sample using the open-source Python package \texttt{michael}.
  \item We measured the slope of a truncated power-law, $\alpha_T$, for the same
  bins of flares. Additionally, we measured $\alpha_T$ as a function of Rossby
  number, $R_0$.
\end{enumerate}

\vspace{3mm}

We thank Darryl Seligman and David Wilson for thoughtful insights and useful
conversations. This work made use of the open-source package,
\textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes
reproducible publications. ADF acknowledges funding from ...
